Title Goes Here

### 2024-05-28 analysis/paper/paper.qmd
update on community word

EEO <- jobdata %>%
  select(equal_employment_opportunity_statement) %>% 
  drop_na

@@

EEO_wordcount <- EEO %>%
  mutate(word_count = str_count(equal_employment_opportunity_statement, "\\S+")) %>%
  print()

ggplot(EEO_wordcount) +
  aes(word_count) +
  geom_histogram()

@@

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE) %>%
  drop_na()

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability","citizenship","ancestry","national origin","nondiscrimination","sex","gender","marital status","genetic information","breastfeeding","sexual orientation","discriminate","transgender status","gender expression","veteran")
count(word, sort = TRUE)

@@

```{r}
ggplot(EEO_clean, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  labs(x = "Words", y = "Frequency", title = "Word Frequency") +
  ylim(10,50)
```

>>>>

EEO <- jobdata %>%
  select(equal_employment_opportunity_statement, year_ad_posted) %>% 
  drop_na

@@

@@

#word count for EEO statement
EEO_wordcount <- EEO %>%
  mutate(word_count = str_count(equal_employment_opportunity_statement, "\\S+")) %>%
  print()

jobdata_EEO_year_tally <-
  EEO_wordcount %>%
  group_by(year_ad_posted,
           word_count) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

ggplot(EEO_wordcount) +
  aes(word_count, year_ad_posted) +
  geom_histogram()

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability","citizenship","national origin","sex","gender","marital status","genetic information","breastfeeding","sexual orientation","transgender status","gender expression","gender identity","ancestry","income assignment for child support","arrest and court record","domestic or sexual violence victim status","national guard absence","visible minorities","aboriginal persons","indigenous","LGBTQ2S+","pregnancy","childbirth","faith","genetic or family medical history","medical condition","nationality","ethnicity","parental status","accent","ethnic","creed","political affiliation","immigration status")

@@

ggplot(EEO_clean_community_word) +
  aes(community_word_tally) +
  geom_histogram()
```
